### 2025-04-25 correlation.qmd
20250425 - organization

## Examples {#sec-correlationExamples}

### Player Height and Fantasy Points {#sec-correlationHeightFantasyPoints}

@@

#### Covariance {#sec-correlationExamplesCovariance}

@@

#### Pearson Correlation {#sec-correlationExamplesPearson}

@@

#### Scatterplot with Best-Fit Line

@@

#### Rank Correlation: Spearman's Rho ($\rho$) {#sec-correlationExamplesSpearman}

@@

#### Partial Correlation {#sec-correlationExamplesPartial}

@@

#### Nonlinear Correlation {#sec-correlationExamplesNonlinear}

@@

#### Correlation Matrix {#sec-correlationExamplesMatrix}

@@

#### Correlogram {#sec-correlationExamplesCorrelogram}

>>>>

## Example: Player Height and Fantasy Points {#sec-correlationHeightFantasyPoints}

@@

### Covariance {#sec-correlationExamplesCovariance}

@@

### Pearson Correlation {#sec-correlationExamplesPearson}

@@

### Scatterplot with Best-Fit Line

@@

### Rank Correlation: Spearman's Rho ($\rho$) {#sec-correlationExamplesSpearman}

@@

### Partial Correlation {#sec-correlationExamplesPartial}

@@

### Nonlinear Correlation {#sec-correlationExamplesNonlinear}

@@

### Correlation Matrix {#sec-correlationExamplesMatrix}

@@

### Correlogram {#sec-correlationExamplesCorrelogram}
